Manuscript Figures for Genome Biology

### 2018-10-11 manuscript_figures/manuscript_figures.Rmd
Swap panel of Fig 1 to include ROC

de5 <- readRDS(file=resfile)
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

@@

# Figure 2C: Total number of discoveries varied across method
p3 <- plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      ylab("Number of Rejections") +
      ggtitle("Rejections by alpha level") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

>>>>

de5 <- readRDS(file=resfile)
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05", "bonf", "fdrreg-e")
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

@@

# Figure 2C: ROC curve
p3 <- plotsim_average(res5d, met=c("FPR", "TPR"),filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      #ylab("Number of Rejections") +
      ggtitle("ROC (FPR vs TPR)") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))
